### 2013-06-14 Tex/chapters/model.tex
kleine Fehler behoben

\subsection{Critical Temperature $T_c$ and Critical Exponents}
\label{ssec:finitesize}
    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection.
    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
    is in very good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
    \begin{figure}[htbp]
        \centering
        \subfigure{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}
        }
        \caption[Binder cumulant fitted with polynom of degree 4]
                {Binder cumulant fitted with polynom of degree 4
                (the errorbars are too small to see)}
        \label{fig:binder_fit_s_0}
    \end{figure}%[vgl. Grafik (villeicht)]
    % The arithmetic average of the intersections are plotted [hier schon?]
    %~ [Und den rest der Auswertung]

>>>>

\subsection{Critical Temperature $T_c$ and Critical Exponents}
\label{ssec:finitesize}
    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    To accomplish the collapse in an semi-automatic and reproduceable
    way with an error estimate, the programm
    \texttt{autoscale.py} \cite{autoscale2009} is used.

    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:collapse_s_0}
                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
                    polynom of degree 4 in vincinity of \(T_c\)
                    (the errorbars are too small to see)}
        \label{fig:binder_fit_s_0}
    \end{figure}
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection.
    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
    is in very good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\

    % The arithmetic average of the intersections are plotted [hier schon?]
    %~ [Und den rest der Auswertung]
